---
title: "The Incomparable Network"
editor_options:
  chunk_output_type: console
---

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)

targets::tar_source()
targets::tar_load(incomparable_episodes)
incomparable <- poddr::gather_people(incomparable_episodes)

inc_navy   <- palette_incomparable[["navy"]]
inc_orange <- palette_incomparable[["orange"]]
inc_dark   <- palette_incomparable[["navy_dark"]]
```

## All-time stats

All shows on the network, first and last episode timeline.

```{r incomparable_network_timeline}
#| fig-height: !expr fig_height_categories(dplyr::n_distinct(incomparable_episodes$show))
#| fig-width: 10
incomparable_episodes |>
  group_by(show) |>
  mutate(
    d_min = min(date),
    d_max = max(date)
  ) |>
  ggplot(aes(x = reorder(show, d_min))) +
  geom_errorbar(aes(ymin = d_min, ymax = d_max),
    width = .5, linewidth = 1, alpha = .85, color = inc_navy
  ) +
  coord_flip() +
  scale_y_continuous(
    transform = c("date", "reverse"),
    breaks = scales::breaks_width("2 years"),
    minor_breaks = scales::breaks_width("1 year"),
    labels = scales::label_date("%Y")
  ) +
  theme_incomparable() +
  theme(axis.text.y = element_text(hjust = 1)) +
  labs(
    x = NULL, y = "First to last episode date",
    title = "The Incomparable Network",
    subtitle = "Show timelines: first and last known episode dates.",
    caption = caption
  )
```


All episodes since 2011.

```{r incomparable_network_alltime_count}
#| fig-height: !expr fig_height_categories(dplyr::n_distinct(incomparable_episodes$show))
#| fig-width: 9
incomparable_episodes |>
  count(show) |>
  ggplot(aes(x = reorder(show, n), y = n)) +
  geom_col(fill = inc_navy) +
  coord_flip() +
  theme_incomparable() +
  labs(
    title = "The Incomparable Network",
    subtitle = "All episodes since 2011, by show.",
    x = NULL, y = "Episodes",
    caption = caption
  )
```

```{r incomparable_network_alltime_duration}
incomparable_episodes |>
  filter(year >= 2011) |>
  ggplot(aes(x = date, y = duration, fill = show)) +
  geom_point(shape = 21, color = "white", alpha = .6, size = 1.8, stroke = 0.2) +
  scale_y_time(breaks = hms::hms(minutes = seq(0, 300, 30))) +
  scale_fill_viridis_d(option = "rocket", guide = "none", end = 0.85) +
  theme_incomparable() +
  labs(
    title = "The Incomparable Network",
    subtitle = "Episode duration over time; one fill per show.",
    x = NULL, y = "Duration (HH:MM)",
    caption = caption
  )
```

```{r incomparable_network_alltime_monthly}
incomparable_episodes |>
  filter(year >= 2011) |>
  count(year, month) |>
  ggplot(aes(x = month, y = n)) +
  geom_point(color = inc_navy, alpha = .8, size = 1.2) +
  facet_wrap(~year, nrow = 1, scales = "free_x") +
  theme_incomparable() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = rel(0.5))) +
  labs(
    title = "The Incomparable Network",
    subtitle = "Episodes per month since 2011.",
    x = NULL, y = "Episodes",
    caption = caption
  )
```

Episode duration by the 15 people most frequently appearing on the network:

```{r top_15_people_duration}
top_15 <- incomparable |>
  filter(year >= 2011) |>
  count(person) |>
  top_n(15) |>
  pull(person)

incomparable |>
  filter(person %in% top_15) |>
  group_by(person) |>
  mutate(mean_duration = mean(duration)) |>
  ggplot(aes(x = reorder(person, mean_duration), y = duration)) +
  geom_point(alpha = .4, position = position_jitter(height = 0, width = .25),
             color = inc_navy, size = 1) +
  geom_boxplot(alpha = .35, outlier.alpha = 0,
               color = inc_dark, fill = palette_incomparable[["cream"]]) +
  coord_flip() +
  theme_incomparable() +
  labs(
    title = "The Incomparable Network",
    subtitle = "Episode duration for the 15 most frequently appearing people.",
    x = NULL, y = "Duration (HH:MM)",
    caption = caption
  )
```


## `r current_year` hosts and guests

```{r currentyear_panelists_network, fig.height=14}
incomparable |>
  filter(year == current_year) |>
  count(person, role) |>
  spread(role, n) |>
  replace_na(list(guest = 0, host = 0)) |>
  mutate(total = guest + host) |>
  arrange(desc(total)) |>
  datatable(style = "bootstrap", colnames = c("Person", "Guest", "Host", "Total Appearances"))
```

I opted to leave out the plot for that data because *oh boy so many people*, so I hope everyone will be happy with the table.
It was artisanally crafted as a gift to *The Incomparable* panelists and fans <3

### A searchable table of all the nice people<small>*</small>

<small>* All the nice people _and_ Philip Mozolak</small>

Here's a searchable and sortable list of all the episodes released in `r current_year` (UTC, no freedom timestamps, sorry). There are multiple rows per episode, because each person gets their own row, which should make it a little easier to find out which person participated in which episode. Because manually searching through <https://www.theincomparable.com/person/> would be almost like work.

```{r currentyear_panelists_network_fulltable}
incomparable |>
  filter(year == current_year) |>
  select(
    show, number, date,
    duration, title, person, role
  ) |>
  mutate(
    date = lubridate::as_date(date),
    show = factor(show)
  ) |>
  arrange(desc(date)) |>
  datatable(
    style = "bootstrap", filter = "top",
    colnames = c(
      "Show", "#", "Date (UTC)",
      "Duration (mins)", "Title", "Person",
      "Role"
    )
  ) |>
  formatDate(3, method = "toDateString")
```

## `r current_year` shows

TL;DR TeeVee is basically cheating.

```{r incomparable_network_currentyear_shows}
#| fig-height: !expr fig_height_categories(dplyr::n_distinct(incomparable_episodes$show[incomparable_episodes$year == current_year]))
#| fig-width: 9
incomparable_episodes |>
  filter(year == current_year) |>
  count(show) |>
  ggplot(aes(x = reorder(show, n), y = n)) +
  geom_col(fill = inc_navy) +
  coord_flip() +
  theme_incomparable() +
  labs(
    title = glue::glue("The Incomparable Network — {current_year}"),
    subtitle = "Shows by episode count.",
    x = NULL, y = "Episodes",
    caption = caption
  )
```

## `r current_year` episodes

```{r incomparable_network_currentyear_episodes, fig.height=6, fig.width=9}
incomparable_episodes |>
  filter(year == current_year) |>
  mutate(date = lubridate::round_date(date, unit = "week")) |>
  count(date) |>
  ggplot(aes(x = date, y = n)) +
    geom_col(fill = inc_navy) +
    scale_x_date(date_breaks = "1 month", date_labels = "%B") +
    theme_incomparable() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    labs(
      title = glue::glue("The Incomparable Network — {current_year}"),
      subtitle = "Episodes per week.",
      x = NULL, y = "Episodes per week",
      caption = caption
    )
```

## Yearly episode output

All in all, *The Incomparable* published `r round(sum(incomparable_episodes$duration) / lubridate::dminutes(1))` minutes of content, or `r round(sum(incomparable_episodes$duration) / lubridate::dweeks(1))` weeks, which are numbers that exist as a concept in your head but not in reality.

```{r incomparable_network_episodes_peryear}
incomparable_episodes |>
  filter(year >= 2011) |>
  count(year) |>
  ggplot(aes(x = factor(year), y = n)) +
    geom_col(fill = inc_navy) +
    theme_incomparable() +
    labs(
      title = "The Incomparable Network",
      subtitle = "Episodes per year.",
      x = NULL, y = "Episodes",
      caption = caption
    )
```
