---
title: "The Mothership"
knitr:
  opts_chunk: 
    fig_path: "plots/incomparable_mothership/"
editor_options: 
  chunk_output_type: console
---

```{r}
#| file: _common.R
#| include: false
```

## Introduction

I would like to do a lot more with this, but currently time is scarce.  
However, I want to fulfill [Jason's request](https://twitter.com/jsnell/status/800412064640483328), since I would love to be worthy of the title of *record keeper*.


```{epoxy tenth-summary, .transformer = epoxy_style_bold()}
Since its first episode on {format(min(as.Date(mothership_wide$date, na.rm = TRUE)), "%B %d, %Y")}, The Incomparable has accumulated {round(sum(mothership_wide$duration, na.rm = TRUE)/dhours(1))} hours of content (roughly {round(sum(mothership_wide$duration, na.rm = TRUE)/ddays(1))} days) across {nrow(mothership_wide)} episodes.
```

The latest episode in the current dataset:

```{r tenth-latest-data}
mothership_wide |>
  head(1) |>
  select(number, date, title, host, guest) |>
  mutate(
    date = as.Date(date),
    title = glue::glue("<a href=\"https://www.theincomparable.com/theincomparable/{number}\">{title}</a>"),
    guest = and::and(stringr::str_split(guest, ";", simplify = TRUE))
  ) |>
  knitr::kable(
    col.names = c("#", "Date", "Title", "Host", "Guests"),
    escape = FALSE
  ) |>
  kableExtra::kable_styling()
```

## Panelists 

### `r current_year` Panelists


```{epoxy panelists-head, .transformer = epoxy_style_bold()}
There were {nrow(filter(mothership_wide, year == current_year))} episodes published in {current_year}. Here's a breakdown by host and guest counts.
```

```{r current_year_panelists_tab, fig.height=9}
mothership_long |>
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$"), year == current_year) |>
  count(person, role) |>
  pivot_wider(names_from = role, values_from = n, values_fill = 0) |>
  mutate(
    person = factor(person),
    total = guest + host,
    total_perc = scales::label_percent(.accuracy = .1)(total / nrow(mothership_wide)),
    rank = rank(-total, ties.method = "min")
  ) |>
  arrange(desc(total)) |>
  select(rank, person, host, guest, total, total_perc) |>
  reactable(
    columns = list(
      rank = colDef(name = "Rank", sortable = TRUE),
      person = colDef(name = "Person", filterable = TRUE, sortable = TRUE),
      host = colDef(name = "Host", sortable = TRUE),
      guest = colDef(name = "Guest", sortable = TRUE),
      total = colDef(name = "Total", sortable = TRUE),
      total_perc = colDef(name = "Total (%)", sortable = TRUE)
    )
  )
```


Looking at it as a bar chart is not really helping I guess but sure why not.

```{r current_year_panelists_plot}
#| fig-height: 9
panelist_breakdown <- mothership_long |>
  filter(year == current_year) |>
  group_by(person, role) |>
  tally() |>
  spread(role, n) |>
  replace_na(list(guest = 0, host = 0)) |>
  mutate(total = guest + host)

panelist_breakdown_long <- panelist_breakdown |>
  gather(role, n, guest, host) 


ggplot(data = panelist_breakdown_long, aes(x = reorder(person, total), y = n, fill = role)) +
  geom_col(color = "black", alpha = .6) +
  coord_flip() +
  scale_y_continuous(breaks = seq(0, 100, 5), minor_breaks = seq(0, 100, 1)) +
  scale_fill_brewer(palette = "Dark2", label = c("Guest", "Host")) +
  labs(
    title = glue::glue("The Incomparable — {current_year}"),
    subtitle = "Panelists by # of Appearances",
    x = "Panelist", y = "# of Appearances", fill = "Role"
  )
```

### All Time Stats

Here are some rankings of panelists (including hosts) across different metrics / subsets.  
Special bonus episodes are not included (507b, 506b, 337b, 173z).

#### By Number of Appearances

Nothing special, just "appears in episode" counts.

```{r tenth-panelists}
mothership_long |>
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) |>
  count(person, role) |>
  pivot_wider(names_from = role, values_from = n, values_fill = 0) |>
  mutate(
    person = factor(person),
    total = guest + host,
    total_perc = scales::label_percent(.accuracy = .1)(total / nrow(mothership_wide)),
    rank = rank(-total, ties.method = "min")
  ) |>
  arrange(desc(total)) |>
  select(rank, person, host, guest, total, total_perc) |>
  reactable(
    columns = list(
      rank = colDef(name = "Rank", sortable = TRUE),
      person = colDef(name = "Person", filterable = TRUE, sortable = TRUE),
      host = colDef(name = "Host", sortable = TRUE),
      guest = colDef(name = "Guest", sortable = TRUE),
      total = colDef(name = "Total", sortable = TRUE),
      total_perc = colDef(name = "Total (%)", sortable = TRUE)
    )
  )
```

<!--
#### By Segment

The segments the dataset knows about, with episode count:

```{r tenth-segments}
mothership_wide |>
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) |>
  count(category, sort = TRUE) |>
  replace_na(replace = list(category = "General")) |>
  knitr::kable()
```

Ranks and % withing each segment.

```{r tenth-panelists-segments}
mothership_long |>
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) |>
  count(category, person, role) |>
  filter(!is.na(category)) |>
  pivot_wider(names_from = role, values_from = n, values_fill = 0) |>
  mutate(
    segment = factor(category), person = factor(person),
    total = guest + host
  ) |>
  group_by(category) |>
  mutate(
    total_perc = round(total / sum(host), 4),
    rank = rank(-total, ties.method = "min")
  ) |>
  arrange(category, desc(total)) |>
  select(category, rank, person, host, guest, total, total_perc) |>
  datatable(
    style = "bootstrap",
    colnames = c("Segment", "Rank", "Person", "Host", "Guest", "Total", "Total %"), 
    rownames = FALSE,
    filter = "top",
    extensions = "RowGroup",
    options = list(
       rowGroup = list(dataSrc = 0),
       pageLength = 50,
       lengthMenu = c(10, 25, 50, 75, 120)
    )
  ) |>
  formatPercentage(columns = 7, digits = 1)
```

--->

#### By Duration of Appearance

Duration per episode in which each person appears, one episode can count towards multiple people's total of course.

```{r tenth-panelists-duration}
mothership_long |>
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) |>
  group_by(person) |>
  summarize(mins = sum(as.numeric(duration)/60)) |>
  mutate(
    mins = round(mins, 1),
    hours = round(mins/60, 1), 
    days = round(hours/24, 1),
    person = factor(person),
    runtime_perc = scales::label_percent(accuracy = .1)(mins / sum(as.numeric(mothership_wide$duration/60))),
    rank = rank(-mins, ties.method = "min")
  ) |>
  arrange(rank) |>
  select(rank, person, runtime_perc, mins, hours, days) |>
  reactable(
    columns = list(
      rank = colDef(name = "Rank", sortable = TRUE),
      person = colDef(name = "Person", filterable = TRUE, sortable = TRUE),
      runtime_perc = colDef(name = "% of All", sortable = TRUE),
      mins = colDef(name = "Minutes", sortable = TRUE),
      hours = colDef(name = "Hours", sortable = TRUE),
      days = colDef(name = "Days", sortable = TRUE)
    )
  )
```


## Runtime

Because that's the easy one.

```{r runtime}
#| fig-width: 10
# column: screen-inset-shaded
tmp <- mothership_wide |>
  mutate(title_long = str_wrap(paste0(number, ": ", title), 20))

ggplot(tmp, aes(x = date, y = duration)) +
  geom_point(alpha = .75) +
  geom_smooth(method = loess, formula = y ~ x, se = FALSE, color = "red") +
  geom_label_repel(
    data = slice_max(tmp, duration, n = 8),
    aes(label = title_long), alpha = .8, size = 3
  ) +
  scale_x_date(
    date_breaks = "1 year", date_labels = "%Y"
  ) +
  scale_y_time(
    breaks = hms(minutes = seq(0, 1e5, 60)),
    limits = c(0, NA)
  ) +
  labs(
    title = "The Incomparable: Mothership",
    subtitle = "Episode runtimes",
    y = "Duration (HH:MM:SS)", x = "Date Published",
    caption = caption
  )
  
```

### By Year

```{r runtime_year}
#| fig-width: 8
# column: screen-inset-shaded
mothership_wide |> 
  ggplot(aes(x = factor(year), y = duration)) +
    geom_point(
      alpha = .75,
      position = position_jitter(height = 0, width = .2)
    ) +
    geom_boxplot(outlier.alpha = 0, alpha = .5) +
    stat_summary(fun = mean, geom = "point", color = "red") +
    scale_y_time(
      breaks = hms(minutes = seq(0, 1e5, 60)),
      limits = c(0, NA)
    ) +
    labs(
      title = "The Incomparable Network: Mothership",
      subtitle = "Episode runtimes",
      y = "Duration (HH:MM:SS)", x = "Year Published",
      caption = caption
    )

```

### Per Person

```{r runtime_person}
#| fig-height: 18
# column: screen-inset-shaded
mothership_long |>
  filter(year >= 2011) |>
  group_by(person) |>
  mutate(mean_duration = mean(duration)) |>
  ggplot(aes(x = reorder(person, mean_duration), y = duration)) +
  geom_point(alpha = .5, position = position_jitter(height = 0, width = .25)) +
  geom_boxplot(alpha = .5, outlier.alpha = 0) +
  coord_flip() +
  labs(
    title = "The Incomparable Mothership",
    subtitle = "Episode runtimes by panelist",
    y = "Duration (HH:MM:SS)", x = "Panelist",
    caption = caption
  )
```

