---
title: "The Incomparable: Network Wide"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output: 
  html_document:
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
source("00_setup.R")

#### Global options ####
knitr::opts_chunk$set(
  fig.path = "assets/plots/incomparable_network/"
)

incomparable_wide <- readRDS("data/incomparable_episodes.rds")
incomparable <- gather_people(incomparable_wide)
```

## All Time Stats

All shows on the network, first and last episode timeline.

```{r incomparable_network_timeline, fig.height=12}
incomparable_wide |>
  group_by(show) |>
  mutate(
    d_min = min(date),
    d_max = max(date)
  ) |>
  ggplot(aes(x = reorder(show, d_min))) +
  geom_errorbar(aes(ymin = d_min, ymax = d_max),
    width = .5, size = 1, alpha = .75, color = "#2C2E6A"
  ) +
  coord_flip() +
  scale_x_discrete(position = "top") +
  labs(
    x = "", y = "First to Last Episode Date",
    title = "The Incomparable Network",
    subtitle = "Show Timelines: First and last known episode dates",
    caption = caption
  )
```


All episodes since 2011.

```{r incomparable_network_alltime}
incomparable_wide |>
  count(show) |>
  ggplot(aes(x = reorder(show, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "The Incomparable Network",
    subtitle = "All Episodes Since 2011 by Show",
    x = "", y = "# of Episodes",
    caption = caption
  )

incomparable_wide |>
  filter(year >= 2011) |>
  ggplot(aes(x = date, y = duration, fill = show)) +
  geom_point(shape = 21, color = "black", alpha = .5) +
  scale_y_time(
    breaks = hms(minutes = seq(0, 300, 30))
  ) +
  scale_fill_viridis_d(option = "A", guide = "none") +
  labs(
    title = "The Incomparable Network",
    subtitle = "All Episodes Since 2011 by Duration, Colored by Show",
    x = "", y = "Duration (mins)",
    caption = caption
  )

incomparable_wide |>
  filter(year >= 2011) |>
  count(year, month) |>
  ggplot(aes(x = month, y = n)) +
  geom_point(color = "black", alpha = .75) +
  facet_wrap(~year, nrow = 1, scales = "free_x") +
  labs(
    title = "The Incomparable Network",
    subtitle = "Episodes per Month Since 2011",
    x = "", y = "# of Episodes",
    caption = caption
  ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = rel(0.5)))
```

Episode duration by the 15 people most frequently appearing on the network:

```{r top_15_people_duration}
top_15 <- incomparable |>
  filter(year >= 2011) |>
  count(person) |>
  top_n(15) |>
  pull(person)

incomparable |>
  filter(person %in% top_15) |>
  group_by(person) |>
  mutate(mean_duration = mean(duration)) |>
  ggplot(aes(x = reorder(person, mean_duration), y = duration)) +
  geom_point(alpha = .5, position = position_jitter(height = 0, width = .25)) +
  geom_boxplot(alpha = .5, outlier.alpha = 0) +
  coord_flip() +
  labs(
    title = "The Incomparable Network",
    subtitle = "15 Most Frequently Appearing People's Episode Duration",
    x = "", y = "Duration (mins)",
    caption = caption
  )
```


## `r current_year`` Hosts and Guests

```{r currentyear_panelists_network, fig.height=14}
incomparable |>
  filter(year == current_year) |>
  group_by(person, role) |>
  tally() |>
  spread(role, n) |>
  replace_na(list(guest = 0, host = 0)) |>
  mutate(total = guest + host) |>
  arrange(desc(total)) |>
  datatable(style = "bootstrap", colnames = c("Person", "Guest", "Host", "Total Appearances"))
```

I opted to leave out the plot for that data because *oh boy so many people*, so I hope everyone will be happy with the table.  
It was artisanally crafted as a gift to *The Incomparable* panelists and fans <3

### A Searchable Table of All The nice People<small>*</small>

<small>* All the nice people _and_ Philip Mozolak</small>

Here's a searchable and sortable list of all the episodes released in `r current_year` (UTC, no freedom timestamps, sorry). There are multiple rows per episode, because each person gets their own row, which should make it a little easier to find out which person aprticipated in which episode. Because manually searching through <https://www.theincomparable.com/person/> would be almost like work.

```{r currentyear_panelists_network_fulltable}
incomparable |>
  filter(year == current_year) |>
  select(
    show, number, date,
    duration, title, person, role
  ) |>
  mutate(
    #duration = round(duration, 2),
    date = lubridate::as_date(date),
    show = factor(show)
  ) |>
  arrange(desc(date)) |>
  datatable(
    style = "bootstrap", filter = "top",
    colnames = c(
      "Show", "#", "Date (UTC)",
      "Duration (mins)", "Title", "Person",
      "Role"
    )
  ) |>
  formatDate(3, method = "toDateString")
```

## `r current_year` Shows

TL;DR TeeVee is basially cheating.

```{r incomparable_network_currentyear_shows}
incomparable_wide |>
  filter(year == current_year) |>
  count(show) |>
  ggplot(aes(x = reorder(show, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = glue::glue("The Incomparable Network — {current_year}"),
    subtitle = "Shows by episode count",
    x = "",
    y = "# of Episodes",
    caption = caption
  )
```

## `r current_year` Episodes

```{r incomparable_network_currentyear_episodes, fig.height=6, fig.width=9}
incomparable_wide |>
  filter(year == current_year) |>
  mutate(date = round_date(date, unit = "week")) |>
  count(date) |>
  ggplot(aes(x = date, y = n)) +
    geom_col() +
    scale_x_date(
      date_breaks = "1 month",
      date_labels = "%B"
    ) +
    labs(
      title = glue::glue("The Incomparable Network — {current_year}"),
      subtitle = "Shows per week",
      x = "",
      y = "# of Episodes per Week",
      caption = caption
    ) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Yearly Episode Output

All in all, *The Incomparable* published `r round(sum(incomparable_wide$duration) / dminutes(1))` minutes of content, or `r round(sum(incomparable_wide$duration) / dweeks(1))` weeks, which are numbers that exists as a concept in your head but not in reality.

```{r incomparable_network_episodes_peryear}
incomparable_wide |>
  filter(year >= 2011) |>
  count(year) |>
  ggplot(aes(x = factor(year), y = n)) +
    geom_col() +
    labs(
      title = "The Incomparable Network",
      subtitle = "Shows per year",
      x = "",
      y = "# of Episodes per Year",
      caption = caption
    )
```

