---
title: "The Incomparable"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output: 
  html_document:
    fig_height: 8
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
source("00_setup.R")

#### Global options ####
knitr::opts_chunk$set(
  fig.path = "assets/plots/incomparable_main/"
)

incomparable_wide <- readRDS("data/incomparable_episodes.rds") %>%
  filter(show == "The Incomparable Mothership")
incomparable <- gather_people(incomparable_wide)
```

## Introduction

I would like to do a lot more with this, but currently time is scarce.  
However, I want to fulfill [Jason's request](https://twitter.com/jsnell/status/800412064640483328), since I would love to be worthy of the title of *record keeper*.


```{glue tenth-summary, .transformer = epoxy_style_bold()}
Since its first episode on {format(min(as.Date(incomparable_wide$date, na.rm = TRUE)), "%B %d, %Y")}, The Incomparable has accumulated {round(sum(incomparable_wide$duration, na.rm = TRUE)/dhours(1))} hours of content (roughly {round(sum(incomparable_wide$duration, na.rm = TRUE)/ddays(1))} days) across {nrow(incomparable_wide)} episodes.
```

The latest episode in the current dataset:

```{r tenth-latest-data}
incomparable_wide %>%
  head(1) %>%
  select(number, date, title, host, guest) %>%
  mutate(date = as.Date(date)) %>%
  knitr::kable()
```

## Panelists 

### `r current_year` Panelists

```{r current_year_panelists, fig.height=9}
incomparable %>%
  filter(year == current_year) %>%
  group_by(person, role) %>%
  tally() %>%
  spread(role, n) %>%
  replace_na(list(guest = 0, host = 0)) %>%
  mutate(total = guest + host) %>%
  arrange(desc(total)) %>%
  datatable(
    style = "bootstrap",
    colnames = c("Person", "Guest", "Host", "Total")
  )

incomparable %>%
  filter(year == current_year) %>%
  group_by(person, role) %>%
  tally() %>%
  spread(role, n) %>%
  replace_na(list(guest = 0, host = 0)) %>%
  mutate(total = guest + host) %>%
  gather(role, n, guest, host) %>%
  {
    ggplot(data = ., aes(x = reorder(person, total), y = n, fill = role)) +
      geom_col(color = "black", alpha = .6) +
      coord_flip() +
      scale_y_continuous(breaks = seq(0, 100, 5), minor_breaks = seq(0, 100, 1)) +
      scale_fill_brewer(palette = "Set1", label = c("Guest", "Host")) +
      labs(
        title = glue::glue("The Incomparable — {current_year}"),
        subtitle = "Panelists by # of Appearances",
        x = "Panelist", y = "# of Appearances", fill = "Role"
      ) +
      theme(legend.position = "top")
  }
```

### All Time Stats

Here are some rankings of panelists (including hosts) across different metrics / subsets.  
Special bonus episodes are not included (507b, 506b, 337b, 173z).

#### By Number of Appearances

Nothing special, just "appears in episode" counts.

```{r tenth-panelists}
incomparable %>%
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) %>%
  count(person, role) %>%
  pivot_wider(names_from = role, values_from = n, values_fill = 0) %>%
  mutate(
    person = factor(person),
    total = guest + host,
    total_perc = round(total / nrow(incomparable_wide), 4),
    rank = rank(-total, ties.method = "min")
  ) %>%
  arrange(desc(total)) %>%
  select(rank, person, host, guest, total, total_perc) %>%
  datatable(
    style = "bootstrap",
    filter = "top",
    colnames = c("Rank", "Person", "Host", "Guest", "Total", "Total %"), 
    rownames = FALSE,
    options = list(
       pageLength = 25,
       lengthMenu = c(10, 25, 50, 100)
    )
  ) %>%
  formatPercentage(columns = 6, digits = 1)
```

#### By Segment (currently defunct)

The segments the dataset knows about, with episode count:

```{r tenth-segments, eval=FALSE,include=FALSE}
incomparable_wide %>%
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) %>%
  count(category, sort = TRUE) %>%
  replace_na(replace = list(category = "General")) %>%
  knitr::kable()
```

Ranks and % withing each segment.

```{r tenth-panelists-segments, eval=FALSE,include=FALSE}
incomparable %>%
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) %>%
  count(category, person, role) %>%
  filter(!is.na(category)) %>%
  pivot_wider(names_from = role, values_from = n, values_fill = 0) %>%
  mutate(
    segment = factor(category), person = factor(person),
    total = guest + host
  ) %>%
  group_by(category) %>%
  mutate(
    total_perc = round(total / sum(host), 4),
    rank = rank(-total, ties.method = "min")
  ) %>%
  arrange(category, desc(total)) %>%
  select(category, rank, person, host, guest, total, total_perc) %>%
  datatable(
    style = "bootstrap",
    colnames = c("Segment", "Rank", "Person", "Host", "Guest", "Total", "Total %"), 
    rownames = FALSE,
    filter = "top",
    extensions = "RowGroup",
    options = list(
       rowGroup = list(dataSrc = 0),
       pageLength = 50,
       lengthMenu = c(10, 25, 50, 75, 120)
    )
  ) %>%
  formatPercentage(columns = 7, digits = 1)
```

#### By Duration of Appearance

Duration per episode in which each person appears, one episode can count towards multiple people's total of course.

```{r tenth-panelists-duration}
incomparable %>%
  # Filter out special episodes containing letters
  filter(!str_detect(number, "[a-z]$")) %>%
  group_by(person) %>%
  summarize(mins = sum(as.numeric(duration)/60)) %>%
  mutate(
    mins = round(mins, 1),
    hours = round(mins/60, 1), 
    days = round(hours/24, 1),
    person = factor(person),
    runtime_perc = round(mins / sum(as.numeric(incomparable_wide$duration/60)), 4),
    rank = rank(-mins, ties.method = "min")
  ) %>%
  arrange(rank) %>%
  select(rank, person, runtime_perc, mins, hours, days) %>%
  datatable(
    style = "bootstrap",
    filter = "top",
    colnames = c("Rank", "Person", "% of All", "Minutes", "Hours", "Days"), 
    rownames = FALSE,
    options = list(
       pageLength = 25,
       lengthMenu = c(10, 25, 50, 100)
    )
  ) %>%
  formatPercentage(columns = 3, digits = 1)
```


## Runtime

Because that's the easy one.

```{r runtime, fig.width=10}
incomparable_wide %>%
  mutate(title_long = str_wrap(paste0(number, ": ", title), 20)) %>%
  {
    ggplot(data = ., aes(x = date, y = duration)) +
      geom_point(alpha = .75) +
      geom_smooth(method = loess, se = F, color = "red") +
      geom_label_repel(
        data = slice_max(., duration, n = 5),
        aes(label = title_long), alpha = .8, size = 3
      ) +
      scale_x_date(
        date_breaks = "1 year", date_labels = "%Y"
      ) +
      scale_y_time(
        breaks = hms(minutes = seq(0, 1e5, 60)),
        limits = c(0, NA)
      ) +
      labs(
        title = "The Incomparable: Mothership",
        subtitle = "Episode runtimes",
        y = "Duration (HH:MM:SS)", x = "Date Published",
        caption = caption
      )
  }
```

### By Year

```{r runtime_year, fig.width=10}
incomparable_wide %>% 
  ggplot(aes(x = factor(year), y = duration)) +
    geom_point(
      alpha = .75,
      position = position_jitter(height = 0, width = .2)
    ) +
    geom_boxplot(outlier.alpha = 0, alpha = .5) +
    stat_summary(fun = mean, geom = "point", color = "red") +
    scale_y_time(
      breaks = hms(minutes = seq(0, 1e5, 60)),
      limits = c(0, NA)
    ) +
    labs(
      title = "The Incomparable Network: Mothership",
      subtitle = "Episode runtimes",
      y = "Duration (HH:MM:SS)", x = "Year Published",
      caption = caption
    )

```

### Per Person

```{r runtime_person, fig.height=15}
incomparable %>%
  filter(year >= 2011) %>%
  group_by(person) %>%
  mutate(mean_duration = mean(duration)) %>%
  ggplot(data = ., aes(x = reorder(person, mean_duration), y = duration)) +
  geom_point(alpha = .5, position = position_jitter(height = 0, width = .25)) +
  geom_boxplot(alpha = .5, outlier.alpha = 0) +
  coord_flip() +
  labs(
    title = "The Incomparable Mothership",
    subtitle = "Episode runtimes by panelist",
    y = "Duration (HH:MM:SS)", x = "Panelist",
    caption = caption
  )
```

