---
title: "Relay.fm — In Numbers"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
#### Global options ####
options(max.print = "75")
opts_chunk$set(echo    = FALSE,
	             cache   = FALSE,
               prompt  = FALSE,
               tidy    = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               fig.retina = 2,
               fig.path = "assets/relay/")
opts_knit$set(width = 75)

#### Data prep ####
source("setup.R")

relay <- readRDS("data/relay.rds") %>% filter(year >= 2014)
shows <- relay %>% group_by(podcast) %>% tally() %>% arrange(desc(n)) %>% extract2("podcast")

relay %<>%
  mutate(podcast = factor(podcast, levels = shows, ordered = T),
         year_num = year(date))

```

After doing [The Incomparable](http://stats.jemu.name/theincomparable/results_incomparable_master.html), I had to go see what I could do with [Relay.fm's](https://relay.fm) data as well, naturally.  
So this is the beginning of that. The source code is included in [this repo](https://github.com/jemus42/podcaststats), and, in case anyone asks:  
Yes, you can use these graphs for whatever. Maybe link back to me, that would be cool.

Please note that there's probably still stuff coming.

# Overview

```{r text_placeholders, echo=F}
lastyear <- relay %>% filter(year == year(now()) - 1) %>% nrow()
thisyear <- relay %>% filter(year == year(now())) %>% nrow()
progress <- round(thisyear/lastyear * 100, 1)
```


[Relay.fm](https://relay.fm/) spans **`r length(shows)`** shows and a combined runtime of over **`r relay$duration %>% sum() %>% divide_by(60) %>% divide_by(24) %>% floor`** days spread across **`r nrow(relay)` episodes** since 2014.  

In `r year(now())-1`, there were **`r lastyear`** episodes published, and we're currently about **`r progress`%** of the way there at **`r thisyear`** episodes this year.

## Shows per Year

```{r show_peryear}
relay %>%
  group_by(podcast, year) %>%
  tally %>%
  ggplot(aes(x = as.factor(year), weight = n, fill = podcast)) +
  geom_bar() +
  scale_y_continuous(breaks = seq(0, 1000, 100),
                     minor_breaks = seq(0, 1000, 25)) +
  scale_fill_viridis(discrete = T) +
  labs(x = "Year", y = "# of Episodes", fill = "Show",
       title = expression(paste(italic("Relay.fm "), "Episodes per Year"))) +
  theme_readthedown(axis_emph = "y") +
  theme(legend.key.size = unit(.5, "cm"))

```

## Shows per Week

```{r shows_perweek}
relay %>%
  mutate(week = week(date),
         year_num = year(date)) %>%
  filter(year_num >= 2014) %>%
  group_by(year, week) %>%
  tally %>%
  {
  ggplot(data = ., aes(x = week, y = n)) +
  geom_point() +
  geom_smooth(data = filter(., year != 2017),
              method = lm, se = F, color = "red") +
  scale_y_continuous(breaks = seq(0, 100, 5),
                     minor_breaks = seq(0, 100, 1)) +
  scale_x_continuous(breaks = seq(0, 55, 16)) +
  facet_wrap(~year) +
  labs(title = expression(paste(italic("Relay.fm "), "Weekly Episode Output")),
       x = "Week of Year", y = "Episodes Published") +
  theme_readthedown(axis_emph = "y")
  }
```

### Regularity

```{r shows_perweek_bars, fig.height=10, fig.width=11}
relay %>%
  mutate(week = isoweek(date),
         year_num = year(date)) %>%
  filter(year_num == 2015) %>%
  group_by(podcast, year, week) %>%
  tally %>%
  ggplot(aes(x = week, weight = n)) +
  geom_bar() +
  scale_y_continuous(breaks = seq(0, 10, 1)) +
  scale_x_continuous(breaks = seq(0, 60, 10)) +
  facet_wrap(~podcast, ncol = 2) +
  labs(title = expression(paste(italic("Relay.fm "), 
                                "Episodes per Week in 2015")),
       x = "Week of Year", y = "# fo Episodes") +
  theme_readthedown(axis_emph = "y") +
  theme(axis.text.y = element_text(size = rel(.5))) 
```

### Regularity and Age

```{r shows_perweek_perage}
relay %>%
  group_by(podcast) %>%
  summarize(first_aired = min(date),
            last_aired = max(date),
            episodes = length(unique(number)),
            duration = sum(duration)) %>%
  mutate(lifetime_weeks = as.numeric(difftime(last_aired, first_aired, units = "weeks")),
         episodes_per_week = episodes / lifetime_weeks,
         duration_per_week = duration / lifetime_weeks) %>%
  ggplot(aes(x = lifetime_weeks, y = episodes_per_week)) +
  geom_point() +
  geom_label_repel(aes(label = podcast), size = 3) +
  geom_hline(aes(yintercept = mean(episodes_per_week)), linetype = "dotted", color = "blue") +
  geom_vline(aes(xintercept = mean(lifetime_weeks)), linetype = "dotted", color = "blue") +
  labs(title = expression(paste(italic("Relay.fm "), 
                                "Show Lifetime and Weekly Output")),
       x = "Lifetime of Podcast in Weeks", y = "Average # of Episodes per Week") +
    theme_readthedown(axis_emph = "y")
```


## Shows per Month

```{r shows_permonth}
relay %>%
  mutate(month = month(date),
         year_num = year(date)) %>%
  filter(year_num >= 2014) %>%
  group_by(year, month) %>%
  tally %>%
  {
  ggplot(data = ., aes(x = month, y = n)) +
  geom_point() +
  geom_smooth(data = filter(., year != 2017),
              method = lm, se = F, color = "red") +
  scale_y_continuous(breaks = seq(0, 100, 15),
                     minor_breaks = seq(0, 100, 5)) +
  scale_x_continuous(breaks = seq(0, 13, 2),
                     minor_breaks = seq(0, 13, 1)) +
  facet_grid(.~year, space = "free_x", scales = "free_x") +
  labs(title = expression(paste(italic("Relay.fm "), "Monthly Episode Output")),
       x = "Month of Year", y = "Episodes Published") +
  theme_readthedown(axis_emph = "y")
  }
```

# Runtimes

## All Shows

```{r runtime_allshows, fig.height=8, fig.width=11}
relay %>%
  filter(podcast != "B-Sides") %>%
  {
    ggplot(., aes(x = date, y = duration)) +
      geom_point() +
      expand_limits(y = 0) +
      scale_x_datetime(breaks = date_breaks("6 months"), minor_breaks = date_breaks("3 month"),
                       date_labels = "%b %Y") +
      scale_y_continuous(breaks = seq(0, 300, 30),
                         minor_breaks = seq(0, 300, 15)) +
      facet_wrap(~podcast, ncol = 7) +
      labs(title = expression(paste(italic("Relay.fm "), "Episode Durations")),
           x = "Date Published", y = "Duration (mins)") +
      theme_readthedown(axis_emph = "y") +
      theme(axis.text.x = element_text(angle = 45, vjust = .5))
  }

```

### Histogram

```{r runtime_allshows_hist, fig.width=7}
relay %>%
  ggplot(aes(x = duration)) +
  geom_histogram(binwidth = 2.5) +
  geom_density(aes(y = ..count.., group = 1), fill = "black", alpha = .3) +
  scale_x_continuous(breaks = seq(0, 300, 15),
                         minor_breaks = seq(0, 300, 5)) +
  scale_y_continuous(breaks = seq(0, 300, 15),
                         minor_breaks = seq(0, 300, 5)) +
  scale_fill_viridis(discrete = T) +
  labs(title = expression(paste(italic("Relay.fm "), "Episode Durations")),
           y = "Frequency", x = "Duration (mins)") +
  theme_readthedown(axis_emph = "y")
```


## Average by Show

### Boxplots 

```{r runtime_avg_pershow}
relay %>%
  #filter(podcast != "B-Sides") %>%
  group_by(podcast) %>%
  mutate(dur_mean = mean(duration)) %>%
         {
           ggplot(., aes(x = reorder(podcast, dur_mean), y = duration)) +
             geom_boxplot() +
             stat_summary(fun.y = "mean", geom = "point", size = 2, color = "red") +
             coord_flip() +
             scale_y_continuous(breaks = seq(0, 300, 30),
                                minor_breaks = seq(0, 300, 15)) +
             labs(title = expression(paste(italic("Relay.fm "), 
                                           "Episode Duration — Boxplot + Mean (red)")),
                  x = "", y = "Duration (mins)") +
             theme_readthedown()
         }

```

### 95% CI

```{r runtime_ci_pershow}
relay %>%
  #filter(podcast != "B-Sides") %>%
  group_by(podcast) %>%
  mutate(dur_mean = mean(duration)) %>%
  {
    ggplot(., aes(x = reorder(podcast, dur_mean), y = duration)) +
      stat_summary(fun.data = "mean_ci_t", geom = "errorbar") +
      stat_summary(fun.y = "mean", geom = "point", size = 2, color = "red") +
      coord_flip() +
      expand_limits(y = 0) +
      scale_y_continuous(breaks = seq(0, 300, 15),
                         minor_breaks = seq(0, 300, 5)) +
      labs(title = expression(paste(italic("Relay.fm "), "Episode Duration — 95% CI + Mean (red)")),
           x = "", y = "Duration (mins)") +
      theme_readthedown()
  }
```
