---
title: "Relay.fm — In Numbers"
date: "`r format(Sys.time(), '%F %R', tz = 'UTC', usetz = T)`"
author: "Lukas — @jemus42"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(knitr)
#### Global options ####
options(max.print = "75")
opts_chunk$set(echo    = FALSE,
	             cache   = FALSE,
               prompt  = FALSE,
               tidy    = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE,
               fig.retina = 2,
               fig.path = "assets/relay/")
opts_knit$set(width = 100)

#### Data prep ####
source("00_setup.R")

relay <- readRDS("data/relay.rds") %>% filter(year >= 2014)
# shows <- relay %>% group_by(podcast) %>% tally() %>% arrange(desc(n)) %>% pull("podcast")

shows <- relay %>% 
  group_by(podcast) %>% 
  summarise(age = min(date)) %>% 
  arrange(age) %>%
  pull("podcast")

relay %<>%
  mutate(podcast = factor(podcast, levels = shows, ordered = T),
         year_num = year(date))
```

After doing [The Incomparable](http://stats.jemu.name/theincomparable/results_incomparable_master.html), I had to go see what I could do with [Relay.fm's](https://relay.fm) data as well, naturally.  
So this is the beginning of that. The source code is included in [this repo](https://github.com/jemus42/podcaststats), and, in case anyone asks:  
Yes, you can use these graphs for whatever. Maybe link back to me, that would be cool.

Please note that there's probably still stuff coming.

# Overview

```{r text_placeholders, echo=F}
lastyear <- relay %>% filter(year == year(now()) - 1) %>% nrow()
thisyear <- relay %>% filter(year == year(now())) %>% nrow()
progress <- round(thisyear/lastyear * 100, 1)
```


[Relay.fm](https://relay.fm/) spans **`r length(shows)`** shows and a combined runtime of over **`r relay$duration %>% sum() %>% divide_by(60) %>% divide_by(24) %>% floor`** days spread across **`r nrow(relay)` episodes** since 2014.  

In `r year(now())-1`, there were **`r lastyear`** episodes published, and we're currently about **`r progress`%** of the way there at **`r thisyear`** episodes this year.

## Shows by Age

```{r shows_byage, fig.height=9}
readRDS("data/relay.rds") %>%
  group_by(podcast) %>%
  mutate(d_min = min(date),
         d_max = max(date)) %>%
  ggplot(aes(x = reorder(podcast, d_min), color = show_status)) +
  geom_errorbar(aes(ymin = d_min, ymax = d_max),
                width = .5, size = 2, alpha = .75) +
  coord_flip() +
  scale_x_discrete(position = "top") +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "", y = "First to Last Episode Date",
       title = "Relay.fm", subtitle = "Show Timelines",
       caption = caption, color = "Status") +
  theme(legend.position = "top")
```

## Shows per Year

```{r show_peryear, fig.height = 6, fig.width = 10}
relay %>%
  group_by(podcast, year) %>%
  tally %>%
  ggplot(aes(x = as.factor(year), weight = n, fill = podcast)) +
  geom_bar() +
  scale_y_continuous(breaks = seq(0, 1000, 100),
                     minor_breaks = seq(0, 1000, 25)) +
  scale_fill_viridis(discrete = TRUE, 
                      guide = guide_legend(ncol = 2, keyheight = 1.5)) +
  labs(x = "Year", y = "# of Episodes", fill = "Show",
       title = "Relay.fm", subtitle = "Episodes per Year",
       caption = caption) +
  theme_ipsum(grid = "y") +
  theme(legend.key.size = unit(.2, "cm"))
```

## Shows per Week

```{r shows_perweek, fig.height=6, fig.width = 10}
relay %>%
  mutate(week = week(date),
         year_num = year(date)) %>%
  filter(year_num >= 2014) %>%
  group_by(year, week) %>%
  tally %>%
  {
  ggplot(data = ., aes(x = week, y = n)) +
  geom_point() +
  geom_smooth(method = lm, se = F, color = "red") +
  scale_y_continuous(breaks = seq(0, 100, 5),
                     minor_breaks = seq(0, 100, 1)) +
  scale_x_continuous(breaks = seq(0, 55, 16)) +
  facet_wrap(~year) +
  labs(title = "Relay.fm", subtitle = "Weekly Episode Output",
       x = "Week of Year", y = "Episodes Published", caption = caption) +
  theme_ipsum(grid = "y")
  }
```

### Regularity

```{r shows_perweek_bars, fig.height=12, fig.width=11}
relay %>%
  mutate(week = isoweek(date),
         year_num = year(date)) %>%
  filter(year_num == 2017) %>%
  group_by(podcast, year, week) %>%
  tally %>%
  ggplot(aes(x = week, y = n)) +
  geom_col() +
  #scale_y_continuous(breaks = seq(0, 10, 1)) +
  #scale_x_continuous(breaks = seq(0, 60, 10)) +
  facet_wrap(~podcast, ncol = 3) +
  labs(title = "Relay.fm", subtitle = "Episodes per Week in 2017",
       x = "Week of Year", y = "# fo Episodes", caption = caption) +
  theme_ipsum(grid = "y") +
  theme(axis.text.y = element_text(size = rel(.5))) 
```


## Shows per Month

```{r shows_permonth}
relay %>%
  mutate(month = month(date),
         year_num = year(date)) %>%
  filter(year_num >= 2014) %>%
  group_by(year, month) %>%
  tally %>%
  {
  ggplot(data = ., aes(x = month, y = n)) +
  geom_point() +
  geom_smooth(method = lm, se = F, color = "red") +
  scale_y_continuous(breaks = seq(0, 100, 15),
                     minor_breaks = seq(0, 100, 5)) +
  scale_x_continuous(breaks = seq(0, 13, 2),
                     minor_breaks = seq(0, 13, 1)) +
  facet_grid(.~year, space = "free_x", scales = "free_x") +
  labs(title = "Relay.fm", subtitle = "Monthly Episode Output",
       x = "Month of Year", y = "Episodes Published", caption = caption) +
  theme_ipsum() +
  theme(axis.text.x = element_text(size = rel(.9)))
  }
```

# Runtimes

## All Shows

```{r runtime_allshows_scatter, fig.height=7, fig.width=10}
relay %>%
  filter(year >= 2011) %>%
  ggplot(aes(x = date, y = duration, color = podcast)) +
  geom_point(alpha = .5) +
  scale_x_date(date_breaks = "1 years",
               date_labels = "%Y",
               date_minor_breaks = "1 month") +
  scale_y_continuous(breaks = seq(0, 300, 60),
                     minor_breaks = seq(0, 300, 15),
                     limits = c(0, NA)) +
  scale_color_viridis(discrete = TRUE, 
                      guide = guide_legend(ncol = 1, keyheight = .75, )) +
  labs(title = "Relay.fm",
       subtitle = "Episode Durations of Every Episode Since 2011",
       x = "Date Published", y = "Duration (mins)", color = "Show",
       caption = caption)
```


```{r runtime_allshows, fig.height=15, fig.width=15}
relay %>%
  filter(podcast != "B-Sides") %>%
  {
    ggplot(., aes(x = date, y = duration)) +
      geom_point() +
      expand_limits(y = 0) +
      scale_x_date(breaks = date_breaks("12 months"), 
                   minor_breaks = date_breaks("6 month"),
                   date_labels = "%Y") +
      scale_y_continuous(breaks = seq(0, 300, 30),
                         minor_breaks = seq(0, 300, 15)) +
      facet_wrap(~podcast, ncol = 5) +
      labs(title = "Relay.fm", subtitle = "Episode Durations",
           x = "Date Published", y = "Duration (mins)", caption = caption) +
      theme_ipsum(grid = "y") +
      theme(axis.text.x = element_text(angle = 90, vjust = .5))
  }
```

### Histogram

```{r runtime_allshows_hist, fig.width=9, fig.height=7}
relay %>%
  ggplot(aes(x = duration)) +
  geom_histogram(binwidth = 2.5) +
  geom_density(aes(y = ..count.., group = 1), fill = "black", alpha = .3) +
  scale_x_continuous(breaks = seq(0, 600, 30),
                     minor_breaks = seq(0, 600, 5)) +
  scale_y_continuous(breaks = seq(0, 600, 50)) +
  labs(title = "Relay.fm", subtitle = "Episode Durations",
           y = "Frequency", x = "Duration (mins)", caption = caption) +
  theme_ipsum(grid = "YX")
```


## Average by Show

### Boxplots 

```{r runtime_avg_pershow, fig.height=9}
relay %>%
  #filter(podcast != "B-Sides") %>%
  group_by(podcast) %>%
  mutate(dur_mean = mean(duration)) %>%
         {
           ggplot(., aes(x = forcats::fct_reorder(podcast, dur_mean), y = duration)) +
             geom_boxplot() +
             stat_summary(fun.y = "mean", geom = "point", size = 2, 
                          color = "black", fill = "red", shape = 21) +
             coord_flip() +
             scale_y_continuous(breaks = seq(0, 300, 30),
                                minor_breaks = seq(0, 300, 15)) +
             labs(title = "Relay.fm", 
                  subtitle = "Episode Duration — Boxplot + Mean (red)",
                  x = "", y = "Duration (mins)", caption = caption) +
             theme_ipsum()
         }
```

# People

Sadly I don't have a lot of data about people besides the hosts of each show. I *could* try to pry out the guests of shows out of each show's RSS feed, but sadly this information is not neatly presented in the feed, but rather would require an amount of regexing I am not prepared, and therefore not able to do.  
Be that as it may, here's a bit about the hosts.

```{r people, fig.height=9}
relay %>%
  separate_rows(people, sep = ",\\s+") %>%
  mutate(people = str_remove(people, ",") %>% str_trim(side = "both")) %>%
  count(people) %>%
  ggplot(aes(x = reorder(people, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(title = "Relay.fm",
       subtitle = "Person by Number of Episodes",
       x = "", y = "# of Episodes Hosted",
       caption = caption)
```

## Host by hours per week of podcasting, says @lbutlr in the slack

Sooo okay!

```{r hosts_by_hours_by_weeks_active, fig.height = 9}
relay %>%
  separate_rows(people, sep = ",\\s+") %>%
  mutate(people = str_remove(people, ",") %>% str_trim(side = "both")) %>%
  group_by(people) %>%
  summarize(
    n = n(), 
    duration = sum(duration), 
    first_show = min(date),
    last_show = max(date),
    weeks_active = first_show %--% last_show / dweeks(1),
    duration_per_week = duration / weeks_active
  ) -> people_activity


ggplot(people_activity, aes(x = reorder(people, duration_per_week), y = duration_per_week)) +
  geom_col() +
  coord_flip() +
  labs(title = "Relay.fm",
       subtitle = "Total duration per host divided by number of weeks active\n(First to latest appearance)",
       x = "", y = "Average Duration (mins)",
       caption = caption)
```

## Period of host activity

```{r relay_people_activity, fig.height = 9}
ggplot(people_activity) +
  geom_segment(aes(x = forcats::fct_reorder(people, first_show, .desc = TRUE), xend = people, 
                   y = first_show, yend = last_show),
               size = 2, alpha = .75) +
  coord_flip() +
  labs(title = "Relay.fm",
       subtitle = "Period of hosting activity (first to most recent show)\nOrdered by first appearance",
       x = "", y = "Date of show",
       caption = caption)
```

