---
title: "Relay FM — In Numbers"
editor_options:
  chunk_output_type: console
---

```{r setup}
#| include: false

library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
library(DT)
library(hms)
library(epoxy)

targets::tar_source()
targets::tar_load(relay_shows)
targets::tar_load(relay_episodes)

relay_episodes <- relay_episodes |>
  left_join(
    relay_shows |> select(show, show_status),
    by = "show"
  )

shows <- relay_episodes |>
  group_by(show) |>
  summarise(age = min(date)) |>
  arrange(age) |>
  pull("show")

relay_episodes <- relay_episodes |>
  mutate(show = factor(show, levels = shows, ordered = TRUE))

relay_anchor <- palette_relayfm[["accent"]]
```

After doing [The Incomparable](http://stats.jemu.name/theincomparable/results_incomparable_master.html), I had to go see what I could do with [Relay FM's](https://relay.fm) data as well, naturally.
So this is the beginning of that. The source code is included in [this repo](https://github.com/jemus42/podcaststats), and, in case anyone asks:
Yes, you can use these graphs for whatever. Maybe link back to me, that would be cool.

Please note that there's probably still stuff coming.

# Overview

```{r text_placeholders}
lastyear <- relay_episodes |>
  filter(year == year(now()) - 1) |>
  nrow()
thisyear <- relay_episodes |>
  filter(year == year(now())) |>
  nrow()
progress <- round(thisyear / lastyear * 100, 1)
```

```{epoxy, .transformer = epoxy_transform_bold()}
[Relay FM](https://relay.fm/) spans {length(shows)} shows and a combined runtime of over {round(sum(relay_episodes$duration, na.rm = TRUE)/ddays(1))} days spread across {nrow(relay_episodes)} episodes since 2014.

In {year(now()) - 1}, there were {lastyear} episodes published, and we're currently about {progress}% of the way there at {thisyear} episodes this year.
```


## Shows by age

```{r shows_by_age}
#| fig-height: !expr fig_height_categories(nrow(relay_shows))
#| fig-width: 10
relay_episodes |>
  group_by(show) |>
  mutate(
    d_min = min(date),
    d_max = max(date)
  ) |>
  ggplot(aes(y = reorder(show, d_min), color = show_status)) +
  geom_errorbar(aes(xmin = d_min, xmax = d_max),
    width = .5, linewidth = 2, alpha = .85
  ) +
  geom_vline(xintercept = as.Date("2014-01-01"), linetype = "dashed", color = "grey60") +
  scale_x_continuous(
    transform = c("date", "reverse"),
    breaks = scales::breaks_width("2 years"),
    minor_breaks = scales::breaks_width("1 year"),
    labels = scales::label_date("%Y")
  ) +
  scale_color_manual(values = c(Active = "#009E73", Retired = "#999999")) +
  theme_relayfm() +
  theme(axis.text.y = element_text(hjust = 1)) +
  labs(
    y = NULL, x = "First to last episode date",
    title = "Relay FM: show timelines",
    caption = caption, color = "Status"
  )
```

## Shows per year

```{r show_per_year, fig.height = 6, fig.width = 10}
relay_episodes |>
  filter(year >= 2014) |>
  group_by(show, year) |>
  tally() |>
  ggplot(aes(x = as.factor(year), weight = n, fill = show)) +
  geom_bar(show.legend = FALSE) +
  scale_y_continuous(
    breaks = seq(0, 1e6, 200),
    minor_breaks = seq(0, 1e6, 100)
  ) +
  scale_fill_viridis_d(option = "mako") +
  theme_relayfm() +
  labs(
    x = "Year", y = "Episodes", fill = NULL,
    title = "Relay FM: episodes per year",
    subtitle = "One color per show; legend omitted at this many shows.",
    caption = caption
  )
```

## Shows per week

```{r shows_per_week, fig.height=6, fig.width = 10}
relay_episodes |>
  mutate(
    week = week(date),
    year_num = year(date)
  ) |>
  filter(year_num >= 2014) |>
  group_by(year, week) |>
  tally() |>
  ggplot(aes(x = week, y = n)) +
    geom_point(color = palette_relayfm[["slate"]], alpha = .6, size = 1.2) +
    geom_smooth(method = lm, formula = y ~ x, se = FALSE,
                color = relay_anchor, linewidth = 0.8) +
    scale_y_continuous(
      breaks = seq(0, 100, 10),
      minor_breaks = seq(0, 100, 5)
    ) +
    scale_x_continuous(breaks = seq(0, 55, 16)) +
    facet_wrap(~year) +
    theme_relayfm() +
    labs(
      title = "Relay FM: weekly episode output",
      x = "Week of year", y = "Episodes published",
      caption = caption
    )
```

### Regularity (TBA)

```{r shows_per_week_bars}
#| fig-height: 12
#| fig-width: 11
#| eval: false

relay_episodes |>
  mutate(
    week = isoweek(date),
    year_num = year(date)
  ) |>
  filter(year_num == current_year) |>
  count(show, year, week) |>
  ggplot(aes(x = week, y = n)) +
  geom_col(fill = palette_relayfm[["slate"]]) +
  facet_wrap(~show, ncol = 3, scales = "free") +
  theme_relayfm() +
  labs(
    title = "Relay FM", subtitle = "Episodes per week in the current year",
    x = "Week of year", y = "Episodes", caption = caption
  )
```


## Shows per month

```{r shows_per_month}
#| fig-width: 12
relay_episodes |>
  mutate(
    month = month(date),
    year_num = year(date)
  ) |>
  filter(year_num >= 2014) |>
  count(year, month) |>
  ggplot(aes(x = month, y = n)) +
    geom_point(color = palette_relayfm[["slate"]], alpha = .6, size = 1.2) +
    geom_smooth(method = lm, formula = y ~ x, se = FALSE,
                color = relay_anchor, linewidth = 0.8) +
    scale_y_continuous(
      breaks = seq(0, 1e6, 10),
      minor_breaks = seq(0, 1e6, 5)
    ) +
    scale_x_continuous(
      breaks = seq(0, 13, 2),
      minor_breaks = seq(0, 13, 1)
    ) +
    facet_grid(. ~ year, space = "free_x", scales = "free_x") +
    theme_relayfm() +
    labs(
      title = "Relay FM: monthly episode output",
      x = "Month of year", y = "Episodes published",
      caption = caption
    )
```

# Runtimes

## All shows

```{r runtime_allshows_scatter}
#| fig-height: 7
#| fig-width: 10

relay_episodes |>
  filter(year >= 2014, duration <= hms::hms(hours = 4)) |>
  ggplot(aes(x = date, y = duration, color = show)) +
  geom_point(alpha = .5, show.legend = FALSE, size = 1.2) +
  scale_x_date(
    date_breaks = "1 years",
    date_labels = "%Y",
    minor_breaks = NULL
  ) +
  scale_y_time(
    breaks = hms::hms(hours = seq(0, 1e6, 1)),
    limits = c(0, NA)
  ) +
  scale_color_viridis_d(option = "mako") +
  theme_relayfm() +
  labs(
    title = "Relay FM: episode durations since 2014",
    subtitle = "One color per show, no legend. Episodes under 4 hours only.",
    x = "Date published", y = "Duration (HH:MM:SS)",
    caption = caption
  )
```


```{r runtime_allshows}
#| fig-height: !expr fig_height_facets(dplyr::n_distinct(relay_episodes$show[relay_episodes$year >= 2014 & relay_episodes$show != "B-Sides"]), ncol = 5)
#| fig-width: 14

relay_episodes |>
  filter(show != "B-Sides", year >= 2014) |>
  ggplot(aes(x = date, y = duration)) +
    geom_point(color = palette_relayfm[["slate"]], alpha = .5, size = 1) +
    expand_limits(y = 0) +
    scale_x_date(
      date_breaks = "12 months",
      date_minor_breaks = "6 month",
      date_labels = "%Y"
    ) +
    scale_y_time(
      breaks = hms::hms(minutes = seq(0, 1e6, 60))
    ) +
    facet_wrap(~show, ncol = 5, scales = "free") +
    theme_relayfm() +
    theme(axis.text.x = element_text(angle = 90, vjust = .5)) +
    labs(
      title = "Relay FM: episode durations by show",
      x = "Date published", y = "Duration (HH:MM:SS)",
      caption = caption
    )
```

### Histogram

```{r runtime_allshows_hist}
#| fig-height: 8
#| fig-width: 11

relay_episodes |>
  filter(duration <= hms::hms(hours = 3)) |>
  ggplot(aes(x = duration)) +
  geom_histogram(binwidth = 120,
                 fill = palette_relayfm[["slate"]], color = "white") +
  scale_x_time(
    breaks = hms::hms(minutes = seq(0, 1e6, 30))
  ) +
  scale_y_continuous(breaks = seq(0, 600, 50)) +
  theme_relayfm() +
  labs(
    title = "Relay FM: episode durations",
    subtitle = "Episodes under 3 hours.",
    y = "Episode count", x = "Duration (HH:MM:SS)",
    caption = caption
  )
```


## Average by show

### Boxplots

```{r runtime_avg_pershow}
#| fig-height: !expr fig_height_categories(dplyr::n_distinct(relay_episodes$show))
#| fig-width: 10

relay_episodes |>
  group_by(show) |>
  ggplot(aes(x = forcats::fct_reorder(show, duration, .fun = mean), y = duration)) +
    geom_boxplot(color = "grey25", fill = "grey95", outlier.size = 0.8) +
    stat_summary(
      fun = "mean", geom = "point", size = 2,
      color = relay_anchor
    ) +
    coord_flip() +
    scale_y_time(
      breaks = hms::hms(minutes = seq(0, 1e6, 60)),
      labels = scales::label_time(format = "%H:%M")
    ) +
    theme_relayfm() +
    labs(
      title = "Relay FM: episode duration by show",
      subtitle = "Boxplot per show; show mean marked in blue.",
      x = NULL, y = "Duration (H:M)",
      caption = caption
    )
```

# People

Sadly I don't have a lot of data about people besides the hosts of each show. I *could* try to pry out the guests of shows out of each show's RSS feed, but sadly this information is not neatly presented in the feed, but rather would require an amount of regexing I am not prepared, and therefore not able to do.
Be that as it may, here's a bit about the hosts.

```{r people}
#| fig-height: !expr fig_height_categories(dplyr::n_distinct(poddr::gather_people(relay_episodes)$person))
#| fig-width: 9

relay_episodes |>
  poddr::gather_people() |>
  count(person) |>
  ggplot(aes(x = reorder(person, n), y = n)) +
  geom_col(fill = palette_relayfm[["slate"]]) +
  coord_flip() +
  theme_relayfm() +
  labs(
    title = "Relay FM: hosts by episode count",
    x = NULL, y = "Episodes hosted",
    caption = caption
  )
```

## Host by hours per week of podcasting

Filtered to episodes airing in 2014 or later.

```{r hosts_by_hours_by_weeks_active}
#| fig-height: !expr fig_height_categories(dplyr::n_distinct(poddr::gather_people(dplyr::filter(relay_episodes, year >= 2014))$person))
#| fig-width: 9

relay_episodes |>
  filter(year >= 2014) |>
  poddr::gather_people() |>
  group_by(person) |>
  summarize(
    n = n(),
    duration = sum(duration, na.rm = TRUE),
    first_show = min(date, na.rm = TRUE),
    last_show = max(date, na.rm = TRUE),
    weeks_active = first_show %--% last_show / lubridate::dweeks(1),
    duration_per_week = as_hms(duration / weeks_active),
    .groups = "drop"
  ) ->
  people_activity


ggplot(people_activity, aes(x = reorder(person, duration_per_week), y = duration_per_week)) +
  geom_col(fill = palette_relayfm[["slate"]]) +
  coord_flip() +
  scale_y_time(
    breaks = hms::hms(minutes = seq(0, 1e6, 60)),
    labels = \(x) stringr::str_extract(as.character(x), "\\d{2}:\\d{2}")
  ) +
  theme_relayfm() +
  labs(
    title = "Relay FM: hours of podcast per active week",
    subtitle = "Total hosting duration divided by weeks from first to most recent appearance.",
    x = NULL, y = "Average duration (HH:MM:SS)",
    caption = caption
  )
```

## Period of host activity

```{r relay_people_activity}
#| fig-height: !expr fig_height_categories(nrow(people_activity))
#| fig-width: 9

ggplot(people_activity) +
  geom_segment(aes(
    x = forcats::fct_reorder(person, first_show, .desc = TRUE), xend = person,
    y = first_show, yend = last_show
  ),
  linewidth = 2, alpha = .85, color = palette_relayfm[["slate"]]
  ) +
  coord_flip() +
  theme_relayfm() +
  labs(
    title = "Relay FM: period of hosting activity",
    subtitle = "First to most recent show; ordered by first appearance.",
    x = NULL, y = "Date of show",
    caption = caption
  )
```
